How fluid-mechanical erosion creates anisotropic porous media

### 2022-06-22 docs/PhysicsPaper/StokesErosion.tex
NM

	Fortunately, it is possible to devise a test to isolate these two types of anisotropy from one another and therefore determine how much each contributes to the total anisotropy. In particular, for a fixed configuration of partially-eroded bodies, we replace each body with a circle having the same area and center of mass. Since the configurations resulted from the erosion of initially circular bodies, such a replacement does not lead to any overlap between bodies. We then measure the two permeabilities, $k_{11}^{(c)}$ and $ k_{22}^{(c)}$, of this configuration of circular bodies. Since all of the individual shapes are identical and isotropic (i.e. circles), the resulting anisotropy is entirely due to the relative positions of the bodies, thus allowing us to define the {\em configurational} anisotropy as $\anis_C = k_{11}^{(c)} / k_{22}^{(c)}$. The total anisotropy, meanwhile, is the product of the shape and configurational anisotropy, $\anis = \anis_S \anis_C$, the latter of which we have measured. We can therefore deduce the shape anisotropy through $\anis_S = \anis/\anis_C$.

@@

We now do stuff

\vsp{2} \nick{To here in editing} \vsp{2}

@@

>>>>

	Fortunately, it is possible to devise a test to isolate these two types of anisotropy and therefore determine how much each contributes to the total anisotropy. In particular, for a fixed configuration of partially-eroded bodies, we replace each body with a circle having the same area and center of mass. Since the configurations resulted from the erosion of initially circular bodies, such a replacement does not lead to any overlap between bodies. We then measure the two permeabilities, $k_{11}^{(c)}$ and $ k_{22}^{(c)}$, of this configuration of circular bodies. Since all of the individual shapes are identical and isotropic (i.e. circles), the resulting anisotropy is entirely due to the relative positions of the bodies, thus allowing us to define the {\em configurational} anisotropy as $\anis_C = k_{11}^{(c)} / k_{22}^{(c)}$. The total anisotropy, meanwhile, is the product of the shape and configurational anisotropy, $\anis = \anis_S \anis_C$, the latter of which we have measured. We can therefore deduce the shape anisotropy through $\anis_S = \anis/\anis_C$.

@@

With the numerical methods in place, we now present results on how fluid-mechanical erosion alters porous-media properties over time. We will first discuss the results from a single simulation and then generalize to statistical results from ensembles of simulations.

\subsection{Single simulation results}

To begin, we discuss a single simulation of 80 bodies eroding in Stokes flow. For reference, the simulation discussed here is the same one shown in Fig.~\ref{fig1}. The initial configuration consists of 80 circular bodies having randomized sizes and positions. The material-removal process alters both the shape of individual bodies as well as the overall structure of the pore network transmitting the flow, as can be seen in Fig.~\ref{fig1}. The initial porosity is $0.4$, which corresponds to a dense packing (see Fig.~\ref{fig1} for a visual), and Fig.~\ref{fig2}(a) shows how the porosity increases over time as the bodies vanish. 
The resistance to flow decreases with this increasing porosity, as shown in Fig.~\ref{fig2}(b)

%\vsp{2} \nick{To here in editing} \vsp{2}

@@

\subsection{Statistics of ensembles of simulations}
